CogSci Analysis

### 2019-02-25 conceptNet-cogsci/Cogsci.Rmd
Commented out cluster randomization experiment.

cluster_randomization_measurements <- run_experiment(
                          languages = languages,
                          measures = measures,
                          aoa_randomizations = c("none"),
                          cluster_randomizations = c(TRUE, FALSE),
                          cluster_counts = 2:5,
                          samples = 50)

saveRDS(cluster_randomization_measurements, "cluster_randomization_measurements.rds")

>>>>

# cluster_randomization_measurements <- run_experiment(
#                           languages = languages,
#                           measures = measures,
#                           aoa_randomizations = c("none"),
#                           cluster_randomizations = c(TRUE, FALSE),
#                           cluster_counts = 2:5,
#                           samples = 50)
# 
# saveRDS(cluster_randomization_measurements, "cluster_randomization_measurements.rds")
